Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs

### 2021-01-20 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
Completed revised proof of lower bound.

	\item Although Theroem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
	application of \eqref{eqn: appr_error} within the proof of Theorem
	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
	\begin{corollary}
		\label{cor: appr}
		Consider instead of
		Algorithm \ref{alg:ppr} using the approximate PPR vector from
		\citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
		corresponding cluster estimate \smash{$\wh{C}$} in the same manner.  Then 
		provided we take 
		\begin{equation}
		\label{eqn: appr_parameter}
		\varepsilon = \frac{1}{25 n(n - 1)\vol_{\Pbb,r}(\mc{C})} ,
		\end{equation}
		under the assumptions of Theorem~\ref{thm:volume_ssd_ub} the upper bound on symmetric set difference in \eqref{eqn:volume_ssd_ub} still
		holds.
	\end{corollary}	
\end{itemize}

@@

\paragraph{Lower bound on symmetric set difference.}

As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is 
sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}. Let
\begin{equation}
\label{eqn:lower_set}
\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
\end{equation}

\begin{theorem}
	\label{thm:ppr_lb}
	Assume the radius $r < \min\set{\frac{1}{40}\rho, \frac{1}{4}\sigma}$, and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 65  
	\Phi_{\Pbb,r}(\mathcal{L})$, and $(L,U) = (0,1)$.  Then, for any 
	\begin{equation*}
	n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2},
		\frac{8}{\epsilon}}, 
	\end{equation*}
	the following statement holds with probability at least $1 - B_3 n \exp\set{-b_3 n}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap 
		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/10$}, such
	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
	\smash{$\wh{C}$} satisfies    
	\begin{equation}
	\label{eqn:ppr_lb}
	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
	\mc{C}^{(1)}[X]) \geq \frac{1}{4} -  C_4 \cdot 
	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(\frac{\rho \sigma}
		{\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
	\end{equation}
	Consequently, if
	\begin{equation*}
	\epsilon^2 \geq \frac{C_4}{8} \cdot \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ 
		\log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}, 
	\end{equation*}
	then with high probability \smash{$\frac{\sigma
			\rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) 
		\geq 1/8$}.    
\end{theorem}

\textcolor{red}{(TODO): Either (preferably) replace $C_4$ by a number, or otherwise say that it is a universal constant.}

>>>>

	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
	application of \eqref{eqn: appr_error} within the proof of Theorem
	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
	\begin{corollary}
		\label{cor: appr}
		Consider instead of
		Algorithm \ref{alg:ppr} using the approximate PPR vector from
		\citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
		corresponding cluster estimate \smash{$\wh{C}$} in the same manner.  Then 
		provided we take 
		\begin{equation}
		\label{eqn: appr_parameter}
		\varepsilon = \frac{1}{25 n(n - 1)\vol_{\Pbb,r}(\mc{C})} ,
		\end{equation}
		under the assumptions of Theorem~\ref{thm:volume_ssd_ub} the upper bound on symmetric set difference in \eqref{eqn:volume_ssd_ub} still
		holds.
	\end{corollary}	
\end{itemize}

@@

\paragraph{Lower bound on symmetric set difference.}
As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is 
sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}. Let
\begin{equation}
\label{eqn:lower_set}
\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
\end{equation}
In what follows, we put
\begin{align*}
C_{3,\delta} & := 768 \cdot (1 + 3\delta),&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
C_{5,\delta} & := \frac{(1 + \delta)^2}{(1 - \delta)^2},&&C_{6,\delta} := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}.
\end{align*}
\begin{theorem}
	\label{thm:ppr_lb}
	Fix $\delta \in (0,1/7)$. Assume the neighborhood graph radius $r < \sigma/2$, that
	\begin{equation}
	\label{eqn:ppr_lb_condition}
	\max\biggl\{C_{3,\delta} \cdot \frac{r}{\rho} \cdot \ln\Bigl(C_{4,\delta} \frac{\rho\sigma}{r^2 \epsilon^2} \Bigr), \frac{C_{5,\delta}}{n} \cdot \frac{\rho \sigma}{r^2 \epsilon^2} \biggr\} < \frac{1}{18}~~\textrm{and}~~n \geq \frac{6 \sigma \rho (1 + \delta)}{(\sigma - 2r)(\rho - r) (1 - \delta)},
	\end{equation} 
	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot   
	\Phi_{n,r}(\mathcal{L}[X])$, and $(L,U) = (0,1)$.  Then the following statement holds with probability at least $1 - B_3 \exp\set{- \delta^2 b_4 n/(3 + \delta)} - n \exp\{-\delta^2 b_5 n/(3 + \delta)\}$: there exists a set $\mc{C}[X]^g$ of large volume, \\ \smash{$\vol_{n,r}(\mc{C}[X]^g \cap 
		\mc{C}^{(1)}[X]) \geq 6\vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/49$}, such
	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
	\smash{$\wh{C}$} satisfies    
	\begin{equation}
	\label{eqn:ppr_lb}
	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
	\mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{6,\delta} \cdot 
	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}
		{\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
	\end{equation} 
\end{theorem}

\textcolor{red}{(TODO): Check that the assumptions of the Theorem match those used in the proof.}
